---
title: "Isabela & Yuri"
site: distill::distill_website
---

<style type="text/css">
.slick-initialized .slick-slide {
    padding: 0;
}
</style>

<style type="text/css">
h1{
font-family: Taviraj;
}
</style>

<style type="text/css">
h2{
font-family: Taviraj;
}
</style>

<style type="text/css">
h3{
text-align: center;
font-family: Taviraj;
}
</style>

<style type="text/css">
h4{
font-family: Taviraj;
text-align: center;
font-size: 23px;
}
</style>


<style type="text/css">
a{
font-size: 17px;
font-family: Taviraj;
}
</style>

<style type="text/css">
.navbar-fixed-top{
position: absolute;
z-index: 2;
}
</style>

<style type="text/css">
  .navbar-brand {
    content:url(https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/imgs/sakura_complete_2.png);
    width:100%; /*width of your image*/
    max-width: 100%;
    margin-top: -5%;
   height:auto; /*height of your image*/
   padding = 0;
  }
}
</style>

<style type="text/css">
   .title{
   font-size: 0px !important;
}
</style>

<style type="text/css">
   .my_text{
   text-align: center;
   font-family: Taviraj;
}
</style>

<style type="text/css">
   img{
   padding: 3px;
   z-index: 1;
   position: relative;
}
</style>



```{r, echo = FALSE}
# Set up the hook
knit_hooks$set(optipng = hook_optipng)
knit_hooks$set(pngquant = hook_pngquant)
```

```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
# essa foto é de 2020
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abr2022","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abr2022")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7', ut.extra='style="margin:20%; display: inline-block;"'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abri2022","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abri2022")
```

```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
# essa foto é de 2020
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abril2022","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abril2022")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7', ut.extra='style="margin:20%; display: inline-block;"'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abrill2022","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abrill2022")
```

```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
# essa foto é de 2020
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/J","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/J")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7', ut.extra='style="margin:20%; display: inline-block;"'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abrill2022","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abrill2022")
```

```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
# essa foto é de 2020
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Set2017","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Set2017")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7', ut.extra='style="margin:20%; display: inline-block;"'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Setem2017","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Setem2017")
```

```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dez2017","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dez2017")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Deze2017","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Deze2017")
```

```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7', ut.extra='style="margin:20%; display: inline-block;"'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dezemb2017","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dezemb2017")
```



```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dezem2017","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dezem2017")
```

```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Jan2018","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Jan2018")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Jane2018","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Jane2018")
```





```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Mar2018","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Mar2018")
```



```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Nove2018","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Nove2018")
```



```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dezem2018","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dezem2018")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dez2018","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dez2018")
```



```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dezemb2018","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Dezemb2018")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Mar2019","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Mar2019")
```



```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Ago2019","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Ago2019")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Mar2020","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Mar2020")
```



```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Ago2020","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Ago2020")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Deze2021","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Deze2021")
```



```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Set2022","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Set2022")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Fev2023","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Fev2023")
```



```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Mar2023","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Mar2023")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Marc2023","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Marc2023")
```



```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abril2023","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abril2023")
```

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abri2023","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Abri2023")

```{r fig.align='right', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Agos2023","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Agos2023")
```



```{r fig.align='left', echo = FALSE, cache = FALSE, dpi = 25, optipng = '-o7'}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,width='48%',...),
    target="_blank"
    )
}
image_link("https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Set2023","https://media.githubusercontent.com/media/isabela-yuri/isabela-yuri.github.io/main/6bc7410d1d5c571c49960a66fb96a54a856e3fb3/fotos/Set2023")
```

